\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{qtree}
\usepackage{verbatim}
\usepackage{array}

\title{Operativsystemer of multiprogrammering \\ Handin 4}
\author{Malte Stær Nissen and\\
        Jacob Daniel Kirstejn Hansen}

\begin{document}
\maketitle

\tableofcontents
\newpage

\section{Overall assumptions}
We've made the following assumptions, on which our implementation depends on:

\begin{itemize}
\item There can't be more than one file system at a time on the disk, in other
words we avoid partitions.
\item We don't perform any consistency checks of the file system, as we assume
that it's always consistent.
\item We assume we won't have to implement functionality to search through
directories, as the buenos kernel doesn't support the use of different
directories. Furthermore there aren't any system calls to create directories.
\end{itemize}

\section{Design decisions}
We've removed the patting of the fat32 filesystem volume name, to make it makes
more sense.  

\section{Important observations}
Unfortunately we didn't make it to implement some of the functions. The system
can however mount a fat32 file system and unmount it. We've made an effort to
try to implement the syscall\_open function, but something was wrong with the
cluster addressing...

\section{List of changes}

\begin{itemize}
\item buenos/proc/syscall.c: System calls trivially implemented.
\item buenos/fs/filesystems.c: Implemented the slim32 system.
\item buenos/fs/module.mk: Added the slim32.c file to the modules.
\item buenos/fs/slim32.c, buenos/fs/slim32.h: Tried to implement the file
system.
\item buenos/yams.conf: Disk section added (commented out in the handin).
\item buenos/compile: Added tests/fs\_open. Now also writes new test file to
the store.file hard drive.
\item buenos/tests/fs\_open.c: Test file for the syscall\_open file. 
\end{itemize}

\section{Time spent}

We have approximately spent 17-20 hours per person.

\end{document}

